---
title: "co2calculatorPACTA2022"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{co2calculatorPACTA2022}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The `co2calculatorPACTA2022` R package provides the functionality to calculate the carbon dioxide (CO2) emission of a building. The calculation is based on the norm SIA 380/1:2009 "Thermische Energie im Hochbau".

## Installation

You can install the `co2calculatorPACTA2022` from the source tarball with:

``` r
install.packages("co2calculatorPACTA2022_1.2.0.tar.gz", repos = NULL, type = "source")
```

## Calculation

In order to calculate the CO2 emissions of a building, `co2calculatorPACTA2022` provides a single function `calculate_emissions`.

```{r example}
# Load package
library(co2calculatorPACTA2022)

# Calculate the CO2 emission of a multi-family house built in 1981, without refurbishments
r <- calculate_emissions(
  area = 1000,
  floors = 4,
  year = 1981,
  utilisation_key = 1,
  climate_code = "KLO",
  energy_carrier = "gasHeating")

# Check result
str(r)
```

Please refer to `help("calculate_emissions")` for further documentation regarding `calculate_emissions`.

## Data

`co2calculatorPACTA2022` includes three datasets. Check their help pages for further details:

- `climate`: `help("climate")`
- `utilisation`: `help("utilisation")`
- `constants`: `help("constants")`

## Source code

The source tarball contains the complete source code and data of the `co2calculatorPACTA2022` R package.
